---
title: Process raw Canada Nutrient File data files into tidy files.
author: Yihan Wu
date: '2019-01-03'
output_format: html_document
vignette: >
  %\VignetteIndexEntry{Process raw Canada Nutrient File data files into tidy files.}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

The Canadian Nutrient Files consist of 11 raw data files. Data files are processed in the order listed on the CNF 2015 Data Structure document. Date columns will be modified to date type, text kept as character, and numeric columns converted to either integer or double types.

```{r}
library(DataPackageR)
library(dplyr)
library(tibble)
```

# Principal Files

## Food Name

```{r}
ca_food_name <- read.csv(project_extdata_path("FOOD NAME.csv"), stringsAsFactors = F, na.strings=c("","NA"))
ca_food_name$FoodDateOfEntry <- as.Date(ca_food_name$FoodDateOfEntry)
ca_food_name$FoodDateOfPublication <- as.Date(ca_food_name$FoodDateOfPublication)
ca_food_name <- as_data_frame(ca_food_name)

```

"FOOD NAME.csv" is read in with additional arguments for na.strings so formatting FoodDateOfEntry and FoodDateOfPublication can be formatted properly into date type. 

## Nutrient Amount

```{r}
ca_nutrient_amount <- as_data_frame(read.csv(project_extdata_path("NUTRIENT AMOUNT.csv"), stringsAsFactors = F))
ca_nutrient_amount$NutrientDateOfEntry<- as.Date(ca_nutrient_amount$NutrientDateOfEntry)

```

## Conversion Factor 

```{r}
ca_conversion_factor<- as_data_frame(read.csv(project_extdata_path('CONVERSION FACTOR.csv'), stringsAsFactors = F))
ca_conversion_factor$ConvFactorDateOfEntry<- as.Date(ca_conversion_factor$ConvFactorDateOfEntry)
```

## Refuse Amount

```{r}
ca_refuse_amount <- as_data_frame(read.csv(project_extdata_path("REFUSE AMOUNT.csv"), stringsAsFactors = F))
ca_refuse_amount$RefuseDateOfEntry <- as.Date(ca_refuse_amount$RefuseDateOfEntry)
```

## Yield Amount 

```{r}
ca_yield_amount <- as_data_frame(read.csv(project_extdata_path("YIELD AMOUNT.csv"), stringsAsFactors = F))

sum(!is.na(ca_yield_amount$X))
sum(!is.na(ca_yield_amount$X.1))
sum(!is.na(ca_yield_amount$X.2))
sum(!is.na(ca_yield_amount$X.3))

ca_yield_amount <- ca_yield_amount[, 1:4]
```

The yield amount dataframe should not have more than 4 columns but appears to have eight when read into R. All four extra columns do not have actual data.

# Support Files

## Food Group

```{r}
ca_food_group <- as_data_frame(read.csv(project_extdata_path("FOOD GROUP.csv"), stringsAsFactors = F))
```

## Food Source

```{r}
ca_food_source <- as_data_frame(read.csv(project_extdata_path("FOOD SOURCE.csv"), stringsAsFactors = F))

sum(!is.na(ca_food_source$X))
sum(!is.na(ca_food_source$X.1))

ca_food_source <- ca_food_source[, 1:4]
```

The food source dataframe should not have more than 4 columns but appears to have six when read into R. The two extra columns do not have actual data.

## Nutrient Name

```{r}
ca_nutrient_name <- as_data_frame(read.csv(project_extdata_path("NUTRIENT NAME.csv"), stringsAsFactors = F))
```

## Nutrient Source

```{r}
ca_nutrient_source <- as_data_frame(read.csv(project_extdata_path("NUTRIENT SOURCE.csv"), stringsAsFactors = F))
```

## Measure Name

```{r}
ca_measure_name <- as_data_frame(read.csv(project_extdata_path("MEASURE NAME.csv"), stringsAsFactors = F))

sum(!is.na(ca_measure_name$X))
sum(!is.na(ca_measure_name$X.1))

ca_measure_name <- ca_measure_name[, 1:3]
```

The measure name data file should have only three columns, but appears to have five when read into R. The last two columns are empty. 

## Refuse Name 

```{r}
ca_refuse_name <- as_data_frame(read.csv(project_extdata_path("REFUSE NAME.csv"), stringsAsFactors = F))
```

## Yield Name 

```{r}
ca_yield_name <- as_data_frame(read.csv(project_extdata_path("YIELD NAME.csv"), stringsAsFactors = F))
```


